---
title: "Creating VCALL barplots"
output: rmarkdown::html_vignette
vignette: >
  %\VignetteIndexEntry{Creating VCALL barplots}
  %\VignetteEngine{knitr::knitr}
  %\usepackage[UTF-8]{inputenc}
  %\VignetteEncoding{UTF-8}
---

```{r setup, include = FALSE}
devtools::load_all()
#library(VCALLplots)
knitr::opts_chunk$set(
  collapse = TRUE,
  comment = "#>"
)
# pkgdown turns your vignettes into a website
```

# Install and load the library

```{r, eval=FALSE}
devtools::install_github("laurabiggins/VCALLplots")
library(VCALLplots)
```

# Import data  

Use `readr::read_tsv()` to import data initially. It should look something like the table below.
The required column is highlighted.

```{r, echo=FALSE}
knitr::kable(head(vcall_eg)) %>% 
  kableExtra::kable_styling(bootstrap_options = "striped", font_size=10) %>% 
  kableExtra::column_spec(17, background = "#84DCC6") %>%
  kableExtra::scroll_box(width = "100%")
  
```
<br>

# Count the vcalls  

Use the `process_vcalls` function. The only required argument is the tibble of imported data.
This table must have a column containing the V calls, by default the column name is assumed 
to be "V_CALL", but if different, this can be specified using the `vcall_col` argument.

```{r}
processed_vcalls <- process_vcalls(vcall_eg)
```
   
OR...
Explicitly specifying the column name:

```{r}
processed_vcalls <- process_vcalls(vcall_eg, vcall_col = "V_CALL")
```

That should produce a table of counts similar to this:

```{r, echo=FALSE}
knitr::kable(head(processed_vcalls))
```

To export this count data, use `readr::write_csv()`.   
For example:
```{r, eval=FALSE}
readr::write_csv(x = processed_vcalls, file = "processed_vcalls.csv")
```

# Create bar plot

The table of counts can be passed directly to the `vcall_barplot` function.

```{r, fig.width=8}
vcall_barplot(processed_vcalls)
```

To show the raw_counts instead of percentages, use the `y_val` parameter.

```{r, fig.width=8}
vcall_barplot(processed_vcalls, y_val = "raw_count")
```
